Abb Analysis

### 2017-02-08 abbDataAnalysis_Script.Rmd
removal of cancel policy clean from analysis
added costs and addt'l models

@@

  str.data$str.act.revenue <- str.data$bookings * str.data$med.rate

@@

  str.data$str.ext.revenue <- (str.data$bookings * str.data$extr.par *
                                  str.data$med.rate)

  str.data$occ.rate <- 1 - (str.data$block.rate + str.data$avail.rate)

  str.data$pot.occ.rate <- (str.data$bookings * str.data$extr.par) / (366 - (366 * str.data$block.rate))

  str.data$str.pot.revenue <- (str.data$pot.occ.rate * 366 * str.data$med.rate)

@@

  ss60 <- which(str.data.ic$cancel.policy == 'Super Strict 60 Days')
  str.data.ic$cancel.policy[ss60] <- 'Strict'
  cpmiss <- which(str.data.ic$cancel.policy == '')
  str.data.ic <- str.data.ic[-cpmiss, ]

>>>>

State gives energy costs at 330 (apt) to 520 (house).  For 2 person in apt that works out to 5 per person per day.  For house of 4 that works out to about 4 per person per day.

@@

  str.data$cpppd <- 4.5
  str.data$avg.guests <- str.data$bedrooms * 1.5

  str.data$str.act.revenue <- ((str.data$bookings * str.data$med.rate) - 
                                 (str.data$bookings * str.data$avg.guests * str.data$cpppd))

@@

  str.data$str.ext.revenue <- ((str.data$bookings * str.data$extr.par *
                                  str.data$med.rate) - 
                                 (str.data$bookings * str.data$avg.guests * 
                                    str.data$cpppd * str.data$extr.par))
  # 
  str.data$occ.rate <- 1 - (str.data$block.rate + str.data$avail.rate)

  str.data$pot.occ.rate <- ((str.data$bookings * str.data$extr.par) / 
    (366 - (366 * str.data$block.rate)))

  str.data$str.pot.revenue <- ((str.data$pot.occ.rate * 366 * str.data$med.rate) - 
                                 (str.data$pot.occ.rate * 366  * str.data$avg.guests *  
                                    str.data$cpppd))

@@

  mod.ext.str <- glm(str.ext.pref~type+as.factor(bedbath),
                     family=binomial(link='logit'),
                     data=str.data.ic)
  mod.pot.str <- glm(str.pot.pref~type+as.factor(bedbath),
                     family=binomial(link='logit'),
                     data=str.data.ic)
```

  mod.ext.loc <- glm(str.ext.pref~type+as.factor(bedbath)+
                                  sub.mrkt,
                     family=binomial(link='logit'),
                     data=str.data.ic)
  mod.pot.loc <- glm(str.pot.pref~type+as.factor(bedbath)+
                                  sub.mrkt,
                     family=binomial(link='logit'),
                     data=str.data.ic)
```

  mod.ext.host <- glm(str.ext.pref~type+as.factor(bedbath)+
                        sub.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      family=binomial(link='logit'),
                      data=str.data.ic)
  mod.pot.host <- glm(str.pot.pref~type+as.factor(bedbath)+
                        sub.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      family=binomial(link='logit'),
                      data=str.data.ic)
```

  mod.ext.str <- lm(str.ext.prem~type+as.factor(bedbath),
                    data=str.data.ic)
  mod.pot.str <- lm(str.pot.prem~type+as.factor(bedbath),
                    data=str.data.ic)

  mod.ext.host <- lm(str.ext.prem~type+as.factor(bedbath)+
                        sub.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict') + suburb,
                      data=str.data.ic)
  mod.pot.host <- lm(str.pot.prem~type+as.factor(bedbath)+
                        sub.mrkt+
                        I(max.guests/bedrooms)+min.stay+
                        I(cancel.policy=='Flexible') + I(cancel.policy=='Strict'),
                      data=str.data.ic)
```
